Analysis paper

### 2021-06-03 analysis/analysis.Rmd
update tables
update plots and tables

```{r}
# create helper function to make table
make_score_table <- function(scores, 
                             group = TRUE, 
                             full_width = TRUE) {
  # copy data, change names, round column values and reduce to sign. digits
  scores <- as.data.table(scores)
  setnames(scores, 
           old = c("horizon", "model", "target_type", "interval_score", "aem", 
                   "relative_skill", "scaled_rel_skill", "sharpness", 
                   "underprediction", "overprediction", "bias", 
                   "50", "90", "location_target", "target_phase"), 
           new = c("Horizon", "Model", "Target", "WIS", "Abs. error", 
                   "rel. skill", "Skill", "Sharpness", 
                   "Underpred.", "Overpred.", "Bias", 
                   "50%-Cov.", "90%-Cov.", "Target", "Target"), 
           skip_absent = TRUE)

@@

  if ("WIS" %in% names(scores)) {
    wis <- names(scores)[grepl("WIS", names(scores))]
    setcolorder(scores, 
                neworder = c("Target", "Horizon", "Model", wis))  
  }

  scores <- scores[order(Target, Horizon)]
  scores[, Horizon := paste(Horizon, "wk ahead")]

@@

@@

distribution_plot_wis <- function(df, x = "interval_score") {
  df %>%
    ggplot(aes_string(y = "model", x = x, 
                      group = "model", fill = "model")) + 
    geom_density_ridges(aes(fill = model), 
                        quantile_lines = TRUE, quantiles = 0.5, 
                        rel_min_height = 0.005, 
                        scale = 0.95, 
                        jittered_points = TRUE, 
                        position = position_points_jitter(width = 0.05, height = 0),
                        point_size = 1.5, 
                        point_shape = 21,
                        #point_shape = '|',
                        point_alpha = 1, 
                        alpha = 0.7) + 
    geom_density_ridges(quantile_lines=TRUE,
                        quantile_fun=function(x,...) mean(x), 
                        linetype = "dotted", 
                        alpha = 0, 
                        scale = 0.95, 
                        rel_min_height = 0.01) +
    scale_fill_manual(values = brewer.pal(name = "Accent", n = 5)[1:5]) + 
    # scale_color_manual(aesthetics = "point_color", 
    #                    values = brewer.pal(name = "Accent", n = 5)[1:5]) + 
    theme(panel.background = element_rect(fill = "#e1f0fe")) +
    theme(legend.position = "bottom") + 
    labs(y = "Model", x = "Weighted interval score") + 
  scale_x_continuous(labels = scales::label_number(suffix = "k", 
                                                   scale = 1e-3, 
                                                   accuracy = NULL))
}

@@

scores[, .(target_count = .N), by = c("target_phase")]

@@

@@

ggsave("plots/distribution_scores_wis.png", pl_wis, height = 10, width = 9)

@@

coverage_tables <- eval_forecasts(
  filtered_data[grepl("2", target)], 
  summarise_by = c("model", "target_phase", "classification", "range"), 
  compute_relative_skill = TRUE, 
  baseline = "Baseline"
)[range %in% c(50, 90), 
                   .(model, target_phase, coverage, classification, range)] %>%
  dcast(formula = ... ~ range, value.var = "coverage")

scores_tables <- eval_forecasts(
  filtered_data[grepl("2", target)], 
  summarise_by = c("model", "target_phase", "classification"), 
  compute_relative_skill = TRUE, 
  baseline = "Baseline"
)

>>>>

```{r}
# create helper function to make table
make_score_table <- function(scores, 
                             group = TRUE, 
                             full_width = TRUE) {
  # copy data, change names, round column values and reduce to sign. digits
  scores <- as.data.table(scores)
  setnames(scores, 
           old = c("horizon", "model", "target_type", "interval_score", "aem", 
                   "relative_skill", "scaled_rel_skill", "sharpness", 
                   "underprediction", "overprediction", "bias", 
                   "50", "90", "location_target", "target_phase"), 
           new = c("Horizon", "Model", "Target", "WIS", "Abs. error", 
                   "rel. skill", "WIS - rel.", "Sharpness", 
                   "Underpred.", "Overpred.", "Bias", 
                   "50%-Cov.", "90%-Cov.", "Target", "Target"), 
           skip_absent = TRUE)

@@

  if (all(c("WIS", "Horizon") %in% names(scores))) {
    wis <- names(scores)[grepl("WIS", names(scores))]
    setcolorder(scores, 
                neworder = c("Target", "Horizon", "Model", wis))  
  }

  if ("Horizon" %in% names(scores)) {
    scores <- scores[order(Target, Horizon)]
    scores[, Horizon := paste(Horizon, "wk ahead")]
  }

@@

# for horizon <= 2
labels <- df[horizon <= 2][order(target_phase, horizon)]$target_phase
table <- make_score_table(df[horizon <= 2, !"target_type"], group = FALSE) %>%
  pack_rows(index = table(labels), indent = FALSE)
save_kable(table, 
           file = here("analysis", "plots", "table-phases-2.png"))

# for horizon > 2
labels <- df[horizon > 2][order(target_phase, horizon)]$target_phase
table <- make_score_table(df[horizon > 2, !"target_type"], group = FALSE) %>%
  pack_rows(index = table(labels), indent = FALSE)
save_kable(table, 
           file = here("analysis", "plots", "table-phases-4.png"))

@@

distribution_plot_wis <- function(df, x = "interval_score") {
  df %>%
    ggplot(aes_string(y = "model", x = x, 
                      group = "model", fill = "model")) + 
    geom_density_ridges(aes(fill = model), 
                        quantile_lines = TRUE, quantiles = 0.5, 
                        rel_min_height = 0.005, 
                        scale = 0.9, 
                        jittered_points = TRUE, 
                        position = position_points_jitter(width = 0.05, height = 0),
                        point_size = 1.5, 
                        point_shape = 21,
                        #point_shape = '|',
                        point_alpha = 1, 
                        alpha = 0.7) + 
    geom_density_ridges(quantile_lines=TRUE,
                        quantile_fun=function(x,...) mean(x), 
                        linetype = "dotted", 
                        alpha = 0, 
                        scale = 0.9, 
                        rel_min_height = 0.01) +
    scale_fill_manual(values = brewer.pal(name = "Accent", n = 5)[1:5]) + 
    # scale_color_manual(aesthetics = "point_color", 
    #                    values = brewer.pal(name = "Accent", n = 5)[1:5]) + 
    theme(panel.background = element_rect(fill = "#e1f0fe")) +
    theme(legend.position = "bottom") + 
    labs(y = "Model", x = "Weighted interval score") + 
  scale_x_continuous(labels = scales::label_number(suffix = "k", 
                                                   scale = 1e-3, 
                                                   accuracy = NULL))
}

@@

scores[, .(target_count = .N), by = c("target_phase", "model")]

@@

scores[, .(n = .N), by = "target_phase"]

@@

ggsave("plots/distribution_scores_wis.png", pl_wis, height = 11, width = 9)

@@

coverage_tables <- eval_forecasts(
  filtered_data[grepl("2", target)], 
  summarise_by = c("model", "target_phase", "classification", "range", "horizon"), 
  compute_relative_skill = TRUE, 
  baseline = "Baseline"
)[range %in% c(50, 90), 
                   .(model, target_phase, coverage, classification, range)] %>%
  dcast(formula = ... ~ range, value.var = "coverage")

scores_tables <- eval_forecasts(
  filtered_data[grepl("2", target)], 
  summarise_by = c("model", "target_phase", "classification", "horizon"), 
  compute_relative_skill = TRUE, 
  baseline = "Baseline"
)
